%-------------------------
% Resume in Latex
% Author : Anusha Srinivasan
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[12pt]{article}
\usepackage[paperwidth=9.8in, paperheight=15in, margin=0.75in]{geometry}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1


%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{1pt}}
  }
}

% Second format with heading and content
\newcommand{\resumeItemTwo}[2]{
  \item\small{
    \textbf{#1}: {#2}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-5pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeItemProjListEnd}{\end{itemize}\vspace{-10pt}}
%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Anusha Srinivasan} \\ \vspace{1pt}
    \small (+91) 94825-45687 $|$ \href{mailto:x@x.com}{\underline{nsh.srnvsn@gmail.com}} $|$ 
    \href{https://linkedin.com/in/...}{\underline{linkedin.com/in/nsh-srnvsn}} $|$
    \href{https://github.com/...}{\underline{github.com/NshSrnvsn}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Georgia Institute of Technology}{}
      {Master of Science in Computer Science (OMSCS)}{Aug. 2024 -- Present}
    \resumeSubheading
      {Ambedkar Institute of Technology}{Bengaluru, India}
      {Bachelor of Information Science and Engineering}{Aug. 2016 -- Oct 2020}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

  % Oracle Experience
  \resumeSubheading
    {Oracle}{Bengaluru, India}
    {Software Engineer I}{June 2020 -- Present}
    \resumeItemListStart
      \resumeItemTwo{Merit-based Incentive Payment System (MIPS)}
        {Spearheaded the design and development of a high-performance data submissions platform for the Centers for Medicare \& Medicaid Services (CMS), enabling seamless ECQM (Electronic Clinical Quality Measures) reporting. Architected a scalable Ruby backend and interactive JavaScript frontend, boosting system reliability and achieving a 25\% increase in analytics accuracy through optimized API services for score plan calculations.}
      \resumeItemTwo{MIPS Value Pathways (MVPs) Application}
        {Led the frontend development team to deliver critical MVP-aligned features ahead of schedule, within a compressed 5-month timeline. Enhanced submission workflows by integrating real-time ECQM compliance checks, significantly improving user efficiency and adaptability to evolving regulatory requirements.}
      
    \resumeItemListEnd

  % Cerner Experience
  \resumeSubheading
    {Cerner}{Bengaluru, India}
    {Software Engineer}{Apr 2021 -- Sept 2023}
    \resumeItemListStart
      \resumeItemTwo {Data Warehouse Tool Application}
        {Enhanced the ReactJS-based data warehouse platform by developing advanced UI components and optimizing backend services. Refactored NodeJS and Express APIs, reducing response times by 18\%. Identified and resolved fortify vulnerabilities, improving security compliance and ensuring seamless Gov. deployments for sensitive healthcare data.}
      \resumeItemTwo{SAML-ADFS Authentication}
        {Led the redesign of legacy C\# and Java authentication systems, integrating SAML-ADFS protocols to enhance security and enable single sign-on functionality. Delivered the transformation ahead of schedule, improving authentication reliability for over 5,000 healthcare providers.}
      \resumeItemTwo{Healthcare Intelligence Dashboard and Automation}
        {Diagnosed and resolved critical bugs, including performance bottlenecks and SQL injection vulnerabilities. Automated manual processes with a Python-based script, reducing manual workflows by 85\% and increasing team productivity. Proactively mitigated 170 critical and high CVEs within 2 months, ensuring adherence to federal security standards and timely deployments.}
    \resumeItemListEnd

  % JP Morgan Chase & Co. Experience
  \resumeSubheading
    {JP Morgan Chase \& Co.}{Bengaluru, India}
    {Software Engineering Intern}{April 2020 -- Oct 2020}
    \resumeItemListStart
      \resumeItem
        {Designed and optimized data feeds to improve stock trading operations and integrated \emph{Perspective}, a real-time data visualization tool. Collaborated on the frontend development of internal trading tools using React and Node.js.}
    \resumeItemListEnd

\resumeSubHeadingListEnd



%-----------PROJECTS-----------
\section{\href{https://github.com/NshSrnvsn}{Projects}}
    \resumeSubHeadingListStart
    \resumeProjectHeading
          {\textbf{Mountain car} $|$ \emph{Python, Gymnasium, numpy}}{Nov 2024}
          \resumeItemListStart
            \resumeItem{Developed an implementation to train an agent to solve the OpenAI Gym Mountain Car environment with Q-Learning, SARSA, Policy iteration and Value iteration. It also contains pre-trained agents for the model-free algorithms.}
          \resumeItemProjListEnd
      \resumeProjectHeading
          {\textbf{WSN Load balancing using Ant Colony Optimization} $|$ \emph{Python, Simulink, Matlab}}{Feb 2020}
          \resumeItemListStart
            \resumeItem{As part of Bachelors project, Implemented a meta-heuristic algorithm to route network traffic, inspired from ant pheromone trails}
          \resumeItemProjListEnd
      \resumeProjectHeading
          {\textbf{Smart Farm} $|$ \emph{Java, Arduino Uno, sensors}}{April 2019}
          \resumeItemListStart
            \resumeItem{Developed irrigation synchronization via moisture detection of soil. Presented at the 5th National Level Techno Exhibition at Dr. AIT}
          \resumeItemProjListEnd
      \resumeProjectHeading
          {\textbf{Image Steganography} $|$ \emph{Python, Tkinter}}{Oct 2018}
          \resumeItemListStart
            \resumeItem{Created a GUI and CLI application for discrete communication using encrypted images.}
          \resumeItemProjListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, SQL, JavaScript, Ruby} \\
     \textbf{Frameworks}{: React, Node.js, SpringBoot, MongoDB, Jest, GraphQL} \\
     \textbf{Machine Learning Libraries}: Scikit-learn, TensorFlow, PyTorch, Keras, Hugging Face Transformers \\
     \textbf{Data Analysis \& Visualization}: Pandas, NumPy, Matplotlib, Seaborn \\
     \textbf{Developer Tools}{: Git, Jenkins, Kubernetes, AWS} 
     
    }}
 \end{itemize}

 %
%-----------EXTRA CURRICULAR SKILLS-----------
\section{Extra-Curriculars}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Section Leader, Code In Place}: Stanford University \\
     \textbf{\href{https://www.womentech.net/user/2294}{Global Ambassador}}: WomenTech Network
    }}
 \end{itemize}

%-----------EXTRA CURRICULAR SKILLS-----------
\section{Certifications}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    \textbf{\href{https://drive.google.com/file/d/1v6m9e7gAltzsUzG6Fdkpsmyiv_AjjYLn/view?usp=sharing}{Data Science \& Machine Learning}}: NPTEL, Indian Institute of Technology, Madras \\
     \textbf{\href{https://certificates.automationanywhere.com/5aebc4c2-6f3d-4f6e-9c75-78654ecf079e}{RPA Bot Developer}}{: Automation Anywhere} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
